\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{tikz}
\usepackage{graphicx}

\usepackage[sfdefault, thin]{roboto}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% -------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
\vspace{-3pt}
\item\small{
    \textbf{#1}{\textbf{:} #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoTitle}[1]{
\item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{4pt}
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    {\small#3} & {\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{}
\newcommand{\resumeSubHeadingListEnd}{}
\newcommand{\resumeItemListStart}{\vspace{3pt}\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\def\ci#1{\textcircled{\resizebox{.5em}{!}{#1}}}
\definecolor{lightblue}{RGB}{60, 200, 225}

\newcommand{\fakesection}[1]{%
  \par\refstepcounter{section}% Increase section counter
  \sectionmark{#1}% Add section mark (header)
  \addcontentsline{toc}{section}{\protect\numberline{\thesection}#1}% Add section to ToC
  % Add more content here, if needed.
}

% -------------------------------------------
%%%%%% CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% ----------HEADING-----------------
\begin{tabularx}{\textwidth}{ X r }
  {\vspace{-32pt}\color{lightblue}{\fontsize{45}{30}\selectfont Sasha Krassovsky}} &
  \begin{tabular}{ r }
    \ci{\faPhone}+1 (425) 614-9499 \\
    \href{https://www.github.com/save-buffer}{\ci{\faGithub}save-buffer} \\
    \href{mailto:krassovskysasha@gmail.com}{\ci{\faEnvelope}krassovskysasha@gmail.com}\\
    \href{https://www.linkedin.com/in/sashka}{\ci{\faLinkedin}linkedin.com/in/sashka}\\
    \\
    \\
  \end{tabular}
\end{tabularx}

\fakesection{Goal}
I'm an engineer passionate in designing and applying novel approaches to make programs run
faster. I am interested in any of low-level optimization, heterogeneous computing, compilers,
and distributed systems. 
\fakesection{Experience}
\resumeSubHeadingListStart

\vspace{2pt}
\resumeSubheading{SingleStore}{Seattle, WA}
{Software Engineer: Query Execution}{June 2020 - Present}
\resumeItemListStart
\resumeItem{AVX-512 Prototype}
{Designed and implemented a prototype of AVX-512-based query execution in SingleStore, a
  natively-distributed database engine used for both transactions and analytics. The prototype
  achieved up to 20\% improvement on TPCH benchmark queries. Details regarding my experience
  can be found on my
  \href{https://www.singlestore.com/blog/a-programmers-perspective/}{blog post}.}
\resumeItem{GPU-based Query Execution}
{Proposed and drafted a design for GPU-based query execution, winning an internal contest
  for so-called ``moonshot ideas''. Prototyped summation on GPUs in an internal hackathon
  achieving a 2.5x speedup over CPU execution, demonstrating the promise of this approach.}
\resumeItem{Regression Hunting}
{Found and fixed several unexplained performance regressions caused by the team switching
  compilers.}
\resumeItem{Code Maintenance}
{Proposed, designed, and implemented a significant refactor of core columnstore code,
  dramatically increasing maintanability and understandability.}
\resumeItem{Intern Mentor}
{Mentored a summer intern who developed heuristics for various runtime decisions during
  query execution.}
\resumeItem{Interviewer}
{Interviewed prospective intern and new-grad candidates in both English and Russian.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubheading
{Facebook}{Menlo Park, CA}
{Software Engineering Intern: Oculus Application Platform Team}{June 2019 - September 2019}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Swift Playgrounds on Windows}
{Implemented an interactive programming environment on Windows mimicking Apple's
  Playgrounds. The program compiles and executes the input Swift code, and exposes an
  interface to develop UIs. Submitted patches to both the Swift compiler
  and LLVM. Source Code at \href{https://www.github.com/save-buffer/swift-repl}
  {github.com/save-buffer/swift-repl}.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubheading
{Bespoke Silicon Group}{Seattle, WA}
{Undergraduate Researcher}{March 2019 - June 2020}
\resumeItemListStart
\vspace{2pt}
\resumeItem{Hammberblade Manycore}
{Created APIs for and tested a RISC-V Manycore CPU. Further, created highly optimized kernels
  for machine learning on the Manycore. Worked on compiler optimization to issue remote
  loads earlier.}
\resumeItem{Thesis: Exploring Single-Core Optimizations for Manycore Architectures}{Explored
  how I optimized kernels and details regarding my compiler optimziation.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubheading
{Husky Robotics}{Seattle, WA}
{Software Team Lead}{June 2018 - October 2019}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Husky Robotics Software Team Lead}
{Helped design and implement the software for a mars rover. Implemented a wide range of
  software from sensors to networking to inverse kinematics to computer vision.  The team
  won 2nd place at the 2019 Canadian Rover Challenge.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubheading
{MemSQL (now known as SingleStore)}{Seattle, WA}
{Software Engineering Intern}{Summer 2017 and 2018}
\resumeItemListStart
\resumeItem{Graphical Explain}
{Created a browser-based visualizer of query plans generated by MemSQL, aiding
  engineers in understanding query plans and its bottlenecks, ultimately allowing for
  more efficient query tuning.}
\resumeItem{Vectorized Aggregation}
{Achieved a 1.8x improvement on analytical workloads such as the TPCH benchmark by
  vectorizing summation using AVX2, improving runtime of internal components by up to 20x.}
\resumeItem{Hash Join Optimization}
{Achieved 2x performance improvement on hash joins involving integer keys, a key usecase for
star-schema workloads.}
\resumeItemListEnd
\resumeSubheading
{Microsoft}{Redmond, WA}
{High School Intern}{June 2016 - August 2016}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Cyberattack Analytics Dashboard}
{Developed a Web Application which visualized statistics on cyberattacks.
  On display in the Cyber-Defense Operations Center.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\fakesection{Education}
\resumeSubHeadingListStart
\vspace{8pt}
\begin{tabular*}{0.97\textwidth}{@{\extracolsep{\fill}}lrr}
  \textbf{University of Washington} & Overall GPA: 3.70 & Seattle, WA \\
  {\small BS Computer Science with Honors} & {\small In-Major GPA: 3.76} & {\small June 2020} \\
  {\small BS Discrete Mathematics} & {\small In-Major GPA: 3.62} & {\small June 2020} \\
\end{tabular*}\vspace{-5pt}

\resumeSubHeadingListEnd

\pagebreak

\fakesection{Coursework}
\resumeSubHeadingListStart

\resumeSubheading
{\color{lightblue}Coursework}{}
{}{}
\vspace{-8pt}
\resumeItemListStart
\resumeItem{Algorithms}
{Proof-based class focusing on using existing techniques to create and prove
new algorithms.}
\resumeItem{Digital Circuit Design}
{Project-based clsas focusing on introducing the basics of Verilog and FPGAs. Created a
  clone of Dance Dance Revolution on an FPGA using an LED matrix and four pushbuttons.}
\resumeItem{Deep Learning on Coursera}
{Introductory online machine learning course taught by Andrew Ng. Homework done in Python,
  with a combination of hand-written and premade machine learning software.}
\resumeItem{Embedded Systems}
{Project-based class focusing on the creation of an embedded operating system. Created
  a medical device using Arduino running a custom scheduler and task queue system.}
\resumeItem{Stanford Compilers on Coursera}
{Introductory online compilers course taught by Prof. Alex Aiken. Implemented a compiler
  for COOL (Classroom Object-Oriented Language) targetting MIPS.}
\resumeItem{3D Graphics at DigiPen Institute of Technology}
{Summer class introducing 3D Graphics, first algebraically and then using linear algebra.
  Implemented a 3D Graphics pipeline from scratch in C (starting only with a SetPixel
  function) which draws colorful cubes, and allows the user to rotate the camera.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\fakesection{Accomplishments}
\resumeSubHeadingListStart

\resumeSubheading
{\color{lightblue}Accomplishments}{}
{}{}
\vspace{-8pt}
\resumeItemListStart
\resumeItem{2017 ACM ICPC Regionals Qualifier}
{Won 6th place at the UW ACM ICPC competition on team MATLAB Indexers, qualifying
  for regionals.}
\resumeItem{Hunt the Wumpus Alumni Challenge 2016 Winner}
{Programmed a game in C\# from scratch and was selected by a panel of judges as the winner for
  having the most polished and most entertaining game. Available at
  \href{https://www.github.com/save-buffer/ShooterGame}{github.com/save-buffer/ShooterGame}}
\resumeItemListEnd
\resumeSubHeadingListEnd


\fakesection{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{\color{lightblue}Projects}{}
{}{}
\vspace{-8pt}
\resumeItemListStart
\resumeItem{Robotics Algorithms}
{Computer vision and inverse kinematics algorithms written for use by the Husky Robotics
  team. Computer vision can locate tennis balls in an image and segment a keyboard into
  keys. The inverse kinematics algorithm was created by myself and another member of the
  team and implemented by me. Available at
  \href{https://github.com/save-buffer/robot\_cv}{github.com/save-buffer/robot\_cv},
  \href{https://github.com/save-buffer/UseArm}{github.com/save-buffer/UseArm}}
\resumeItem{Slang}
{Compiler for a low-level functional declarative language (like Erlang) written in C.
Available at \href{https://github.com/save-buffer/slang}{github.com/save-buffer/slang}}
\resumeItem{SashCopter}
{An attempt at controlling a drone using an EEG Headset. Main drone control software is
  written. Mind-controlled aspect deemed unsuccessful due to the lack of resolution on
  the headset.  
  \href{https://www.github.com/save-buffer/SashCopter}{github.com/save-buffer/SashCopter}}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
